Testing Quasar Unification with Clumpy Wind Models

### 2015-12-08 paper.tex
about to change order

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/lx_a05_pre.png}
\caption
{
X-ray ($2$~keV) luminosity of the our clumped model (red squares) 
and the H13 model (purple squares), plotted against monochromatic luminosity 
at 2500\AA. The points are labeled according to inclination; angles
$>70^\circ$ correspond to BALs in our scheme (see figure 4).
Also plotted are the samples considered by Saez et al. 2012 on a similar plot; 
The COMBI-7 AGN and the BQS samples Steffen et al. (2006) and the Saez et al. (2012) 
sample of BALQSOs. The dotted line shows the best fit relation for non-BALQSOs 
from Steffen et al. (2006).
}
\label{fig:xray}
\end{figure*} %fullpage

>>>>

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/lx_a05_pre.png}
\caption
{
X-ray ($2$~keV) luminosity of the our clumped model (red squares) 
and the H13 model (blue squares), plotted against monochromatic luminosity 
at 2500\AA. The points are labeled according to inclination; angles
$>70^\circ$ correspond to BALs in our scheme (see figure 4).
Also plotted are masurements from 
the COMBI-7 AGN and the BQS samples (Steffen et al. 2006) and the Saez et al. (2012) 
sample of BALQSOs. The dotted line shows the best fit relation for non-BALQSOs 
from Steffen et al. (2006).
}
\label{fig:xray}
\end{figure*} %fullpage
